An open reproducible framework for the study of the iterated prisoner's dilemma

### 2016-04-01 tex/paper.tex
Adding contributors list.

@@

% All devs (alphabetic order of last name)
\author[2]{James Campbell}
\author[5]{Thomas Campbell}
\author[2]{Alex Carney}
\author[2]{Martin Chorley}
\author[1]{Cameron Davidson-Pilon}
\author[1]{Kristian Glass}
\author[1]{Tom{\'a}{\v s} Ehrlich}
\author[1]{Martin Jones}
\author[4]{Georgios Koutsovoulos}
\author[1]{Holly Marissa}
\author[1]{Jochen M{\"u}ller}
\author[2]{Geraint Palmer}
\author[3]{Paul Slavin}
\author[2]{Timothy Standen}
\author[1]{Luis Visintini}
\author[1]{Karl ?}

@@

\begin{enumerate}
    \item Cooperator
    \item Defector
    \item ZD-Extort-2
    \item Joss: 0.9
    \item Hard Tit For Tat
    \item Hard Tit For 2 Tats
    \item Tit For Tat
    \item Grudger
    \item Tit For 2 Tats
    \item Win-Stay Lose-Shift
    \item Random: 0.5
    \item ZD-GTFT-2
    \item GTFT: 0.33
    \item Hard Prober
    \item Prober
    \item Prober 2
    \item Prober 3
    \item Calculator
    \item Hard Go By Majority
\end{enumerate}

@@

>>>>

\usepackage{multicol}

@@

% All devs (alphabetic order of last name)
\author[2]{James Campbell}
\author[5]{Thomas Campbell}
\author[2]{Alex Carney}
\author[2]{Martin Chorley}
\author[1]{Cameron Davidson-Pilon}
\author[1]{Kristian Glass}
\author[1]{Tom{\'a}{\v s} Ehrlich}
\author[1]{Martin Jones}
\author[4]{Georgios Koutsovoulos}
\author[1]{Holly Marissa}
\author[1]{Jochen M{\"u}ller}
\author[2]{Geraint Palmer}
\author[3]{Paul Slavin}
\author[2]{Timothy Standen}
\author[1]{Luis Visintini}
\author[1]{Karl Molden}

@@

\begin{multicols}{3}
    \begin{enumerate}
        \item Cooperator
        \item Defector
        \item ZD-Extort-2
        \item Joss: 0.9
        \item Hard Tit For Tat
        \item Hard Tit For 2 Tats
        \item Tit For Tat
        \item Grudger
        \item Tit For 2 Tats
        \item Win-Stay Lose-Shift
        \item Random: 0.5
        \item ZD-GTFT-2
        \item GTFT: 0.33
        \item Hard Prober
        \item Prober
        \item Prober 2
        \item Prober 3
        \item Calculator
        \item Hard Go By Majority
    \end{enumerate}
\end{multicols}

@@

\section{Availability}\label{sec:availability}

\subsection{Operating system}

The Axelrod library runs on all major operating systems: Linux, Mac OSX and
Windows.

\subsection{Programming language}

The library is continuously tested for Python 2.7, 3.3, 3.4 and 3.5.

\subsection{Additional system requirements}

There are no specific additional system requirements.

\subsection{Support}

Support is readily available in multiple forms:

\begin{itemize}
    \item An online chat channel:
        \url{https://gitter.im/Axelrod-Python/Axelrod}.
    \item An  email group:
        \url{https://groups.google.com/forum/#!topic/axelrod-python}.
\end{itemize}

\subsection{Dependencies}

The following Python libraries are required dependencies:

\begin{multicols}{3}
    \begin{itemize}
        \item Numpy 1.9.2:
        \item Matplotlib 1.4.2:
        \item Cloudpickle  0.1.1:
        \item Hypothesis  3.0:
        \item Testfixtures  4.9.1:
    \end{itemize}
\end{multicols}

\subsection{List of contributors}

The names of all the contributors are not known: as these were mainly done
through github and certain have not provided their name or responded to a
request for further details. Here is an incomplete list:

\begin{multicols}{3}
    \begin{itemize}
        \item {Owen Campbell}
        \item {Mark Harper}
        \item {Vincent Knight}
        \item {Karol Langner}
        \item {James Campbell}
        \item {Thomas Campbell}
        \item {Alex Carney}
        \item {Martin Chorley}
        \item {Cameron Davidson-Pilon}
        \item {Kristian Glass}
        \item {Tom{\'a}{\v s} Ehrlich}
        \item {Martin Jones}
        \item {Georgios Koutsovoulos}
        \item {Holly Marissa}
        \item {Jochen M{\"u}ller}
        \item {Geraint Palmer}
        \item {Paul Slavin}
        \item {Timothy Standen}
        \item {Luis Visintini}
        \item {Karl Molden}
        \item {Jason Young}
        \item {Andy Boot}
        \item {Anna Barriscale}
    \end{itemize}
\end{multicols}

\subsection{Archive}
\subsection{Code repository}

\section{Reuse potential}\label{sec:reuse}
